Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-05-02 article.tex
Revised paragraph about experiment selection

The second step (Fig.~\ref{fig:pipeline}, 3)
selects an inference model $I$ from a set of inference models $I_{1},\dots,I_{n}$. 
We define an experiment $X_{i}$ as the combination of an inference model $I_{i}$ and the conditions $C_{i}$ to actually use it in the inference step.

Any inference model is composed by a tree\_prior, a clock\_model and a site\_model. 
The inference conditions are composed by two main elements called model\_type and run\_if. They determine how to choose the basic elements composing the inference model that is going to be used in the following of the \verb;pirouette;'s pipeline.
The simplest setup is to use the same site\_model and clock\_model used in the alignment simulation and the same tree\_prior used in the creation of the given phylogeny. We label this model\_type as "generative". In any other case we are dealing with a "candidate" model\_type.
The argument run\_if determines whether the proposed model has to be used or not. If the model\_type is generative it will always be used. If, instead, one or more candidate models are proposed, the user can either let \verb;pirouette; select it as the best among all the candidate models (run\_if == "best\_candidate"), or force its selection (run\_if == "always"). A 'best' model is defined as the inference model with
the highest evidence (a.k.a. marginal likelihood), given the alignment simulated in the previous step.
The evidence of an inference model is estimated by nested sampling [\cite{maturana2018model}], using the \verb;NS; BEAST2 package. Scripted use of BEAST2 packages is only possible under Linux and Mac.
Windows systems can do the model comparison for shorter DNA sequences using the web interface of \verb;mcbette; [\cite{mcbette}].
\iffalse
Even if the model selection is not performed, the user can still estimate the evidence of each proposed inference model by setting "do\_measure\_evidence" to be TRUE.
\fi

>>>>

The second step (Fig.~\ref{fig:pipeline}, 3)
selects one or more inference models $I$ from a set of inference 
models $I_{1},\dots,I_{n}$. 
We define an experiment $X_{i}$ as the combination of 
an inference model $I_{i}$ and the conditions $C_{i}$ 
to actually use it in the inference step.
For example, we can express that an inference
model (a combination of a tree prior, clock model and site model) 
is known to include the generative/true tree prior and that 
we definitely want to use that model in our inference. 
As a second example, wwe can also express that we've submitted a set of 
candidate inference models,
of which only the best should be used in the actual inference.
In the first example, we specified the condition $C_{i}$ that this
generative model should always be run, where in the second example,
we specified condition $C_{i}$ that a candidate model should only be run
when being the best.
A 'best' model is defined as the inference model with
the highest evidence (a.k.a. marginal likelihood), given the alignment 
simulated in the previous step.
The evidence of an inference model is estimated by nested 
sampling [\cite{maturana2018model}], using the \verb;NS; BEAST2 package. 
Scripted use of BEAST2 packages is only possible under Linux and Mac.
Windows systems can do the model comparison for shorter DNA sequences 
using the web interface of \verb;mcbette; [\cite{mcbette}].
